MCDA-EVSE

### 2024-05-12 code/MCDA-EVSE.Rmd
add a topsis method trial

@@

@@

>>>>

```{r}
# reverse is min
weights <- c(0.2, 0.15, 0.1, 0.15, 0.2, 0.1, 0.05, 0.05)
criteriaMinMax <- c("min", "max", "max", "min", "max", "min", "min", "max")
overall1 <- TOPSIS(performanceTable, weights, criteriaMinMax)
TOPSIS <- data.frame(uniqueID = names(overall1), values = overall1) %>%  
  mutate(uniqueID = as.integer(uniqueID)) %>%

TOPSIS_toplot <- fishnet_nowater %>% 
  left_join(TOPSIS, by = "uniqueID")

@@

ggplot()+
  geom_sf(data=fishnet, color="black", fill="white") +
  geom_sf(data=TOPSIS_toplot, color="black", aes(fill=values))

@@

```{r}
summary(TOPSIS$values)
```
